Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-09-09 date/paper.tex
Cut relation partly

\subsubsection{Relation}
Table~\ref{tab:relation} displays the number of clone classes found for the entire corpus for the identified relations between clone instances (see Sec.~\ref{sec:relation}).

\begin{table}[H]
\centering
\begin{tabular}{@{}llrr@{}}
\toprule
\textit{\textbf{Category}} & \textit{\textbf{Relation}} & \textit{\textbf{Clone Classes}} & \textit{\textbf{Total}} \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Class\end{tabular}} & Same Class & 22,893 & \multirow{2}{*}{31,848} \\ \cmidrule(lr){2-3}
 & Same Method & 8,955 &  \\ \midrule
\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Hierarchy\end{tabular}} & Sibling & 15,588 & \multirow{5}{*}{20,342} \\ \cmidrule(lr){2-3}
 & Superclass & 2,616 &  \\ \cmidrule(lr){2-3}
 & First Cousin & 1,219 &  \\ \cmidrule(lr){2-3}
 & Common Hierarchy & 720 &  \\ \cmidrule(lr){2-3}
 & Ancestor & 199 &  \\ \midrule
\multirow{4}{*}{Unrelated} & No Direct Superclass & 10,677 & \multirow{4}{*}{20,314} \\ \cmidrule(lr){2-3}
 & External Superclass & 4,525 &  \\ \cmidrule(lr){2-3}
 & External Ancestor & 3,347 &  \\ \cmidrule(lr){2-3}
 & No Indirect Superclass & 1,765 &  \\ \midrule
\multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Common\\ Interface\end{tabular}} & Same Direct Interface & 7,522 & \multirow{2}{*}{13,074} \\ \cmidrule(lr){2-3}
 & Same Indirect Interface & 5,552 &  \\ \bottomrule
\end{tabular}
\caption{Number of clone classes per clone relation}
\label{tab:relation}
\end{table}

>>>>

\subsubsection{Relation}
We tested to what extent the relation between clone instances in a clone class (see Sec.~\ref{sec:relation}) has an influence on the maintainability of refactored clones.
